A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach to be subject. In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies. And in the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}. In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.

>>>>

Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach. In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies. In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}. In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.
